Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-14 paper/paper.tex
4.3.4 comments

\subsubsection{Frequency of content modifiers.} As previously
mentioned, \percRulesWithContent\ of Suricata rules involve content
options. Furthermnore, we observed that many of these rules indicate
what parts of the message the content string should be checked
against.\Mar{Lucas, (1) vc. tem dados para dar suporte a isto (de http
  e tcp)? ou seja, quantas options do tipo ``content'' possuem
  modificadores.}  For example, the creator of the rule may want to
indicate that a specific string be present in the header of an HTTP
request message. Content \emph{modifiers} serve this purpose. For
example, the modifier \CodeIn{http\_header} in the option
\CodeIn{content: ``keep-alive''; http\_header} states the requirement that
the string ``keep-alive'' be present in the header of the message. (A
keep-alive connection attribute indicates that a single TCP connection
should remain open for multiple HTTP requests/responses.)
Figure~\Fix{adicione pequena figura...verifique se ainda faz sentido
  depois do que falei acima...}

Suricata supports content modifiers for tcp and http. Given that
content options often use modifiers\Mar{assumindo que eh
  verdade. confirmar estat. solicitada acima...}, \tname\ uses
associated frequency to discriminate more or less likely rules. For
example, historical data indicates that content options that use the
\CodeIn{http\_connection} modifiers are much less likely than content
options that use the modifier
\CodeIn{http\_uri}. Figure~\ref{fig:distribution-content_modifiers}
shows the distribution of content modifiers for http. We ommit the
distribution for tcp for space. Similarly to the the previous
heuristic functions, this function uses the frequency of content
modifiers to calibrate the contribution of each rule.

>>>>

\subsubsection{Frequency of content modifiers.} As previously
mentioned, \percRulesWithContent\ of Suricata rules involve content
options. Furthermnore, we observed that many of these rules indicate
what parts of the message the content string should be checked
against.\Mar{Lucas, (1) vc. tem dados para dar suporte a isto (de http
  e tcp)? ou seja, quantas options do tipo ``content'' possuem
  modificadores.} \Luc{conseguirei esses dados} For example, the creator of the rule may want to
indicate that a specific string be present in the header of an HTTP
request message. Content \emph{modifiers} serve this purpose. For
example, the modifier \CodeIn{http\_header} in the option
\CodeIn{content: ``keep-alive''; http\_header} states the requirement that
the string ``keep-alive'' be present in the header of the message. (A
keep-alive connection attribute indicates that a single TCP connection
should remain open for multiple HTTP requests/responses.)
Figure~\Fix{adicione pequena figura...verifique se ainda faz sentido
  depois do que falei acima...}

Suricata supports content modifiers for tcp and http. \Luc{Eh possivel utilizar os modificadores em qualquer protocolo. Nós consideramos apenas tcp e http pois são os protocolos que possuem payloads legiveis, assim conseguimos saber melhor como tokenizar o conteudo. O payload de pacotes de outros protocolos, em geral, são um conjunto de bytes sem significado para nós. Existem diversos outros modificadores q não estamos considerando e q tambem permitem procurar numa determinada posição para os casos em q o conteudo do pacote n eh legivel, não citei pq não suportamos isso. Se necessário posso explicar.} Given that
content options often use modifiers\Mar{assumindo que eh
  verdade. confirmar estat. solicitada acima...}, \tname\ uses
associated frequency to discriminate more or less likely rules. For
example, historical data indicates that content options that use the
\CodeIn{http\_connection} modifiers are much less likely than content
options that use the modifier
\CodeIn{http\_uri}. Figure~\ref{fig:distribution-content_modifiers}
shows the distribution of content modifiers for http. We ommit the
distribution for tcp for space. Similarly to the the previous
heuristic functions, this function uses the frequency of content
modifiers to calibrate the contribution of each rule.
